\texttt{Taxonomic supertree construction with}\texttt{\emph{ Incertae sedis}}\texttt{ taxa}

### 2018-04-25 doc/incertae_sedis.tex
Try another rewording.

First, this approach results in a less-resolved tree because taxonomic
vagueness (in the form of the \emph{incertae sedis} annotation) is interpreted as
an unwarranted statement that the \emph{incertae sedis} taxa are disallowed from
being members of their sibling taxa.  When an incertae sedis taxon is placed within
a sibling taxon by input phylogenies, this is taken as a rejection of the monophyly
of the sibling taxon, which is then removed from the synthesis tree.  For
example, in the synthesis tree in Fig. \ref{fig:Handling-incertae-sedis}c, the
placement of taxon $C$ in group $AB$ is interpreted as a rejection of the
monophyly of $AB$. The edge leading to $AB$ is therefore not incorporated into
the synthesis tree.  In contrast, the synthesis tree in Fig.
\ref{fig:Handling-incertae-sedis}d that does not reject the monophyly of $AB$
retains the grouping of $A$ and $B$.

Second, this approach results in the removal of clade names for all clades that
have an \emph{incertae sedis} taxon place within them.  For example, in Fig.
\ref{fig:Handling-incertae-sedis}c the names for the clades $A$ and $AB$ are lost.

Third, this approach cannot use information from phylogenies to resolve the
location of uncertain taxa.  For example, the synthesis tree in
\ref{fig:Handling-incertae-sedis}c has lost the label for $A$, and so does not
allow us to place $C$ within $A$.  In contrast, the synthesis tree in Fig.
\ref{fig:Handling-incertae-sedis}d that takes account of \emph{incertae sedis}
annotations and retains the label for $A$.  This allows us to infer that
\emph{incertae sedis} taxon $C$ has been placed within $A$, resolving
the uncertainty.

>>>>

This approach incorrectly treats the intrusion of an \emph{incertae sedis} taxon
into a sibling taxon as a conflicting with monophyly of the sibling taxon. For
example, in Fig. \ref{fig:Handling-incertae-sedis}, the placement of the
\emph{incertae sedis} taxon $C$ within $A$ and $AB$, is considered
to contradict the monophyly of $A$ and $AB$ and thus to conflict with those taxa.
This has three main effects.  These effects are illustrated in the difference
between the synthesis tree in Fig. \ref{fig:Handling-incertae-sedis}c, which
ignores \emph{incertae sedis} annotations, and the synthesis tree in Fig.
\ref{fig:Handling-incertae-sedis}d, which respects them.

First, this approach results in a less-resolved tree.  While input trees are
free to place incertae sedis taxa within a sibling, the naive approach
interprets this placement as conflict with the sibling.  Since the taxonomy
is ranked below all input trees, conflict is always resolved in favor of the
input trees, and so the sibling in the taxonomy is removed from the synthesis
tree.  For example, in the synthesis tree in Fig.
\ref{fig:Handling-incertae-sedis}c, the placement of taxon $C$ in group $AB$ is
interpreted as a rejection of the monophyly of $AB$. The edge leading to $AB$ is
therefore not incorporated into the synthesis tree.  In contrast, the synthesis
tree in Fig. \ref{fig:Handling-incertae-sedis}d that does not reject the
monophyly of $AB$ retains the grouping of $A$ and $B$.

Second, this approach results in the removal of clade names for all clades that
have an \emph{incertae sedis} taxon placed within them.  For example, in Fig.
\ref{fig:Handling-incertae-sedis}c the names for the clades $A$ and $AB$ are lost.

Third, this approach cannot use information from phylogenies to resolve the
location of uncertain taxa.  For example, the synthesis tree in
\ref{fig:Handling-incertae-sedis}c has lost the label for $A$, and so does not
allow us to note that $C$ has been placed within $A$.  In contrast, the
synthesis tree in Fig. \ref{fig:Handling-incertae-sedis}d retains the label for
$A$, which allows us to resolve taxonomic uncertainty by infering that
\emph{incertae sedis} taxon $C$ has been placed within $A$.
